Enhancement of SDR in Thessaloniki

### 2024-04-11 high_aod/GHI_enh_02_ID_CE_.tex
Commit 2024-04-11 12:14

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-04-10}

@@

{
\hypersetup{linkcolor=}
\setcounter{tocdepth}{4}
\tableofcontents
}
\begin{verbatim}
[1] "/home/athan/MANUSCRIPTS/02_enhancement/high_aod"
\end{verbatim}

@@

\begin{verbatim}
 [1] "Exact_B.High_W.edir"  "Exact_B.High_W.edn"   "Exact_B.High_W.eup"   "Exact_B.Low_2_W.edir"
 [5] "Exact_B.Low_2_W.edn"  "Exact_B.Low_2_W.eup"  "Exact_B.Exact_W.edir" "Exact_B.Exact_W.edn" 
 [9] "Exact_B.Exact_W.eup"  "Exact_B.Low_W.edir"   "Exact_B.Low_W.edn"    "Exact_B.Low_W.eup"   
\end{verbatim}

@@

\begin{Shaded}
\begin{Highlighting}[]
\ControlFlowTok{switch}\NormalTok{(csmodel,}
       \AttributeTok{Exact\_B.Exact\_W =}\NormalTok{ \{ C4\_cs\_ref\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.02}\NormalTok{; C4\_GLB\_diff\_THRES }\OtherTok{\textless{}{-}} \DecValTok{55}\NormalTok{; C4\_lowcut\_sza }\OtherTok{\textless{}{-}} \DecValTok{60}\NormalTok{; C4\_lowcut\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.12}\NormalTok{\},}
       \AttributeTok{Low\_2\_B.Low\_2\_W =}\NormalTok{ \{ C4\_cs\_ref\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.03}\NormalTok{; C4\_GLB\_diff\_THRES }\OtherTok{\textless{}{-}}  \DecValTok{5}\NormalTok{; C4\_lowcut\_sza }\OtherTok{\textless{}{-}} \DecValTok{60}\NormalTok{; C4\_lowcut\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.12}\NormalTok{\},}
       \AttributeTok{Low\_B.Exact\_W   =}\NormalTok{ \{ C4\_cs\_ref\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.04}\NormalTok{; C4\_GLB\_diff\_THRES }\OtherTok{\textless{}{-}} \DecValTok{20}\NormalTok{; C4\_lowcut\_sza }\OtherTok{\textless{}{-}} \DecValTok{60}\NormalTok{; C4\_lowcut\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.12}\NormalTok{\},}
       \AttributeTok{Low\_B.High\_W    =}\NormalTok{ \{ C4\_cs\_ref\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.05}\NormalTok{; C4\_GLB\_diff\_THRES }\OtherTok{\textless{}{-}} \DecValTok{20}\NormalTok{; C4\_lowcut\_sza }\OtherTok{\textless{}{-}} \DecValTok{60}\NormalTok{; C4\_lowcut\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.12}\NormalTok{\},}
       \AttributeTok{Low\_B.Low\_W     =}\NormalTok{ \{ C4\_cs\_ref\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.05}\NormalTok{; C4\_GLB\_diff\_THRES }\OtherTok{\textless{}{-}}  \DecValTok{0}\NormalTok{; C4\_lowcut\_sza }\OtherTok{\textless{}{-}} \DecValTok{60}\NormalTok{; C4\_lowcut\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.18}\NormalTok{\},}
       \AttributeTok{High\_B.Low\_W    =}\NormalTok{ \{ C4\_cs\_ref\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.10}\NormalTok{; C4\_GLB\_diff\_THRES }\OtherTok{\textless{}{-}}  \DecValTok{0}\NormalTok{; C4\_lowcut\_sza }\OtherTok{\textless{}{-}} \DecValTok{60}\NormalTok{; C4\_lowcut\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.25}\NormalTok{\}, }\DocumentationTok{\#\# same as the used criterio}
\NormalTok{                         \{ C4\_cs\_ref\_ratio }\OtherTok{\textless{}{-}} \DecValTok{1}\NormalTok{   ; C4\_GLB\_diff\_THRES }\OtherTok{\textless{}{-}}  \DecValTok{0}\NormalTok{; C4\_lowcut\_sza }\OtherTok{\textless{}{-}}  \DecValTok{0}\NormalTok{; C4\_lowcut\_ratio }\OtherTok{\textless{}{-}} \DecValTok{1}\NormalTok{   \})}
\DocumentationTok{\#\# init flag}
\NormalTok{DATA[, Enhanc\_C\_4 }\SpecialCharTok{:=} \ConstantTok{FALSE}\NormalTok{]}

@@

\begin{verbatim}
 [1]        NA        NA 1.0440020 0.9584892 0.8852695 0.8218832 0.7664852 0.7176648 0.6743248
[10] 0.6355989 0.6007941
\end{verbatim}

@@

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/unnamed-chunk-10-1} \end{center}

@@

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/unnamed-chunk-13-1} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/unnamed-chunk-13-2} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/unnamed-chunk-13-3} \end{center}

@@

\begin{longtable}[]{@{}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.1389}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.1389}}@{}}
\caption{Enhanc\_C\_4}\tabularnewline
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedleft
FALSE
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
TRUE
\end{minipage} \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedleft
FALSE
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
TRUE
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
6031301 & 170866 \\
\end{longtable}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/unnamed-chunk-13-4} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/unnamed-chunk-13-5} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/unnamed-chunk-13-6} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/unnamed-chunk-13-7} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/unnamed-chunk-13-8} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/unnamed-chunk-13-9} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/unnamed-chunk-13-10} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/unnamed-chunk-13-11} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/unnamed-chunk-13-12} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/unnamed-chunk-13-13} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/unnamed-chunk-13-14} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/unnamed-chunk-13-15} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/unnamed-chunk-13-16} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/unnamed-chunk-13-17} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/unnamed-chunk-13-18} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/unnamed-chunk-13-19} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/unnamed-chunk-13-20} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/unnamed-chunk-13-21} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/unnamed-chunk-13-22} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/unnamed-chunk-13-23} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/unnamed-chunk-13-24} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/unnamed-chunk-13-25} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/unnamed-chunk-13-26} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/unnamed-chunk-13-27} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/unnamed-chunk-13-28} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/unnamed-chunk-13-29} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/unnamed-chunk-13-30} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/unnamed-chunk-13-31} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/unnamed-chunk-13-32} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/unnamed-chunk-13-33} \end{center}

@@

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-1} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-2} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-3} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-4} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-5} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-6} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-7} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-8} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-9} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-10} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-11} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-12} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-13} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-14} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-15} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-16} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-17} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-18} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-19} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-20} \end{center}

@@

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-21} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-22} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-23} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-24} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-25} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-26} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-27} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-28} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-29} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-30} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-31} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-32} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-33} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-34} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-35} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-36} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-37} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-38} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-39} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-40} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-41} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-42} \end{center}

>>>>

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-04-11}

@@

{
\hypersetup{linkcolor=}
\setcounter{tocdepth}{4}
\tableofcontents
}
\begin{Shaded}
\begin{Highlighting}[]
\DocumentationTok{\#\# \_\_ Document options {-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}}
\end{Highlighting}
\end{Shaded}

@@

\begin{verbatim}
 [1] "Exact_B.High_W.edir"  "Exact_B.High_W.edn"   "Exact_B.High_W.eup"  
 [4] "Exact_B.Low_2_W.edir" "Exact_B.Low_2_W.edn"  "Exact_B.Low_2_W.eup" 
 [7] "Exact_B.Exact_W.edir" "Exact_B.Exact_W.edn"  "Exact_B.Exact_W.eup" 
[10] "Exact_B.Low_W.edir"   "Exact_B.Low_W.edn"    "Exact_B.Low_W.eup"   
\end{verbatim}

@@

\begin{Shaded}
\begin{Highlighting}[]
\ControlFlowTok{switch}\NormalTok{(csmodel,}
       \AttributeTok{Exact\_B.Exact\_W =}\NormalTok{ \{ C4\_cs\_ref\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.02}\NormalTok{; C4\_GLB\_diff\_THRES }\OtherTok{\textless{}{-}} \DecValTok{55}\NormalTok{; C4\_lowcut\_sza }\OtherTok{\textless{}{-}} \DecValTok{60}\NormalTok{; C4\_lowcut\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.12}\NormalTok{\},}
       \AttributeTok{Low\_2\_B.Low\_2\_W =}\NormalTok{ \{ C4\_cs\_ref\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.03}\NormalTok{; C4\_GLB\_diff\_THRES }\OtherTok{\textless{}{-}}  \DecValTok{5}\NormalTok{; C4\_lowcut\_sza }\OtherTok{\textless{}{-}} \DecValTok{60}\NormalTok{; C4\_lowcut\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.12}\NormalTok{\},}
       \AttributeTok{Low\_B.Exact\_W   =}\NormalTok{ \{ C4\_cs\_ref\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.04}\NormalTok{; C4\_GLB\_diff\_THRES }\OtherTok{\textless{}{-}} \DecValTok{20}\NormalTok{; C4\_lowcut\_sza }\OtherTok{\textless{}{-}} \DecValTok{60}\NormalTok{; C4\_lowcut\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.12}\NormalTok{\},}
       \AttributeTok{Low\_B.High\_W    =}\NormalTok{ \{ C4\_cs\_ref\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.05}\NormalTok{; C4\_GLB\_diff\_THRES }\OtherTok{\textless{}{-}} \DecValTok{20}\NormalTok{; C4\_lowcut\_sza }\OtherTok{\textless{}{-}} \DecValTok{60}\NormalTok{; C4\_lowcut\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.12}\NormalTok{\},}
       \AttributeTok{Low\_B.Low\_W     =}\NormalTok{ \{ C4\_cs\_ref\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.05}\NormalTok{; C4\_GLB\_diff\_THRES }\OtherTok{\textless{}{-}}  \DecValTok{0}\NormalTok{; C4\_lowcut\_sza }\OtherTok{\textless{}{-}} \DecValTok{60}\NormalTok{; C4\_lowcut\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.18}\NormalTok{\},}
       \AttributeTok{High\_B.Low\_W    =}\NormalTok{ \{ C4\_cs\_ref\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.10}\NormalTok{; C4\_GLB\_diff\_THRES }\OtherTok{\textless{}{-}}  \DecValTok{0}\NormalTok{; C4\_lowcut\_sza }\OtherTok{\textless{}{-}} \DecValTok{60}\NormalTok{; C4\_lowcut\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.30}\NormalTok{\}, }\DocumentationTok{\#\# same as the used criterio}
\NormalTok{                         \{ C4\_cs\_ref\_ratio }\OtherTok{\textless{}{-}} \DecValTok{1}\NormalTok{   ; C4\_GLB\_diff\_THRES }\OtherTok{\textless{}{-}}  \DecValTok{0}\NormalTok{; C4\_lowcut\_sza }\OtherTok{\textless{}{-}}  \DecValTok{0}\NormalTok{; C4\_lowcut\_ratio }\OtherTok{\textless{}{-}} \DecValTok{1}\NormalTok{   \})}
\DocumentationTok{\#\# init flag}
\NormalTok{DATA[, Enhanc\_C\_4 }\SpecialCharTok{:=} \ConstantTok{FALSE}\NormalTok{]}

@@

\begin{verbatim}
 [1]        NA        NA 1.0857621 0.9949418 0.9171711 0.8498384 0.7909847
 [8] 0.7391123 0.6930560 0.6518963 0.6148972
\end{verbatim}

@@

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-10-1} \end{center}

@@

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-1} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-2} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-3} \end{center}

@@

\begin{longtable}[]{@{}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.1389}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.1389}}@{}}
\caption{Enhanc\_C\_4}\tabularnewline
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedleft
FALSE
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
TRUE
\end{minipage} \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedleft
FALSE
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
TRUE
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
6054123 & 148044 \\
\end{longtable}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-4} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-5} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-6} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-7} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-8} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-9} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-10} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-11} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-12} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-13} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-14} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-15} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-16} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-17} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-18} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-19} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-20} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-21} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-22} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-23} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-24} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-25} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-26} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-27} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-28} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-29} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-30} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-31} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-32} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/unnamed-chunk-13-33} \end{center}

@@

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-1} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-2} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-3} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-4} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-5} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-6} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-7} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-8} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-9} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-10} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-11} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-12} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-13} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-14} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-15} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-16} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-17} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-18} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-19} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-20} \end{center}

@@

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-21} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-22} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-23} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-24} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-25} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-26} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-27} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-28} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-29} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-30} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-31} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-32} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-33} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-34} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-35} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-36} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-37} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-38} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-39} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-40} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-41} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE__files/figure-latex/example_days-42} \end{center}
